---
output: 
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
library(ggplot2)
knitr::opts_chunk$set(echo = F)
```

There are a few steps involved in simulating occupancy & SCR data, outlined below:

* Defining the state space
* Simulating activity centers from the defined state space
* Defining the expected *use* of space by each activity center, based on a function of space
* Simulating *use* based on the expectation, in a Poisson random fashion
* Thinning *use* by a certain amount and removing individual ID to obtain occupancy data
* Thinning occupancy information by a certain amount and compressing to presence absence *of individuals* at a trap on an occasion to obtain SCR data

We demonstrate each of these in the document below.

# Simulation of activity centers

Animal activity centers are simulated to be uniformly distributed across <a href="https://www.codecogs.com/eqnedit.php?latex=\mathcal{S}" target="_blank"><img src="https://latex.codecogs.com/gif.latex?\mathcal{S}" title="\mathcal{S}" /></a>, which is the state space of all possible locations for the animal activity centers that could have generated the data. 


## Definition of the state space 

Right after the seed is referenced, there is a section creating this state space. 

```{r, echo = F, eval = T}
X=expand.grid(3:9,3:9)
buff = 3
grid.space = 0.5
```

```{r, echo = T, eval = T}
# Define the state-space by buffering the traps
xmin<- min(X[,1])-buff
xmax<- max(X[,1])+buff
ymin<- min(X[,2])-buff
ymax<- max(X[,2])+buff
```

You will notice that this portion of the script is dependent upon `X`, which is the object holding the locations for the traps, `buff`, which is a buffer around those locations in `X`. What does this look like? Well, say that the traps are just oriented in a regular fashion somewhere near the origin, like so:

```{r}

ggplot() + 
  geom_point(aes(x = X[,1], y = X[,2])) + 
  geom_vline(xintercept = c(xmin, xmax)) + 
  geom_hline(yintercept = c(ymin, ymax)) + 
  coord_equal()

```